Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-17 manuscript/climate_sensitivity_draft.Rmd
switched figs 2 & 3
#115

In the years for which we have vertical profiles in climate data (2016-2018), taller trees--or those in dominant crown positions-- were generally exposed to higher evaporative demand during the peak growing season months (May-August; Fig. **3**). Specifically, maximum daily wind speeds were significantly higher above the top of the canopy (40-50m) than within and below (10-30m) (Fig. **3a**). Relative humidity was also somewhat lower during June-August, ranging from ~50-80% above the canopy and ~60-90% in the understory (Fig. **3b**). Air temperature did not vary across the vertical profile (Fig. **3c**).

Crown position varied as expected with height (dominant > co-dominant > intermediate > suppressed), but with substantial variation (Fig. **3d**). 
Correlation between height and canopy position was 0.73.

@@

At the community level, cored trees showed substantial growth reductions in all three droughts, with a mean $Rt$ of 0.86 in 1966 and 1999, and 0.84 in 1977  (Fig. **1b**). Across the entire study period (1950-2009), the focal drought years were the three years with the largest fraction of trees exhibiting $Rt \le 0.7$. Specifically, in each drought, roughly 30% of the cored trees had growth reductions of $\ge$ 30% ($Rt \le 0.7$): 29% in 1966, 32% in 1977, and 27% in 1999. However, some individuals exhibited increased growth, *i.e.*, $Rt > 1.0$: 26% of trees in 1966, 22% in 1977, and 26% in 1999.

Responses varied across species and by drought (Fig. 2). 
Averaged across all droughts, $Rt$ was lowest in *Liriodendron tulipifera* (mean $Rt$ = **0.66**) and highest in *Fagus grandifolia* (mean $Rt$ = **0.99**).

@@

Wood density, $LMA$, and xylem porosity were all poor predictors of $Rt$ (Tables 1,S4-S5). 
Wood density and $LMA$ were never significantly associated with $Rt$ in the single-variable tests and were therefore excluded from the full models. 
Xylem porosity was also excluded from the full models, as it had no significant influence for all droughts combined and had contrasting effects in the individual droughts: whereas ring-porous species had higher $Rt$ than diffuse- and semi-ring- porous species in the 1966 and 1999 droughts, they had lower $Rt$ in 1977 (Table S4). 
It is noteworthy that the two diffuse-porous species in our study, *Liriodendron tulipifera* and *Fagus grandifolia*, were at opposite ends of the $Rt$ spectrum (Fig. **2**), further refuting the idea that xylem porosity is a useful predictor of $Rt$ in the context of this study.

In contrast, $PLA_{dry}$, and $\pi_{tlp}$ were linked to drought responses (Fig. **4**; Tables 1,S4-S7). 
Both had consistent signs across all droughts and explained modest amounts of variation ($\Delta$AICc > 1.0) during at least one of the three droughts (Table S4), qualifying them as candidate variables for the full model. 
$PLA_{dry}$ had a significant influence, with negative coefficient, in full models for the three droughts combined and for the 1966 drought individually (Fig. 4; Tables S6-S7). 
For 1977 and 1999, it was included, with negative coefficient, in some of the top models (Tables S6-S7).
$\pi_{tlp}$ was included, with negative coefficient, in the best model for all droughts combined and for the 1977 drought individually (Fig. **4**; Table S6). 
It was included in some of the top models for 1999 (Tables S6-S7).

@@

Tree height, microenvironment, and hydraulic traits shaped tree growth responses across three droughts at our study site (Table 1, Fig. **4**). The greater susceptibility of larger trees to drought, similar to forests worldwide [@bennett_larger_2015], was driven primarily by their height [@stovall_tree_2019]. Taller height was likely a liability in itself, and was also associated with greater exposure to conditions that would promote water loss and heat damage during drought (Fig. **3**). There was no evidence that soil water availability increased drought resistance; in contrast, trees in wetter topographic positions had lower $Rt$ [@zuleta_drought-induced_2017; @stovall_tree_2019], and the larger potential rooting volume of large trees provided no advantage in the drier microenvironments. The negative effect of height on $Rt$ held after accounting for species' traits. Drought resistance was not consistently linked to species' $LMA$, wood density, or xylem type (ring- vs. diffuse porous), but was negatively correlated with leaf hydraulic traits ($PLA_{dry}$, $\pi_{tlp}$). This is the first report to our knowledge linking $PLA_{dry}$ and $\pi_{tlp}$ to growth reduction during drought. The directions of these responses were consistent across droughts (Table S6), supporting the premise that they were driven by fundamental physiological mechanisms. However, the strengths of each predictor varied across droughts (Fig. **4**; Tables S6-S7), indicating that drought characteristics interact with tree size, microenvironment, and traits to shape which individuals are most affected. These findings advance our knowledge of the factors that make trees vulnerable to growth declines during drought--and, by extension, likely make them more vulnerable to mortality [@sapes_plant_2019].

The droughts considered here were of a magnitude that has occurred with an average frequency of approximately once every 10-15 years (Fig. **1a**, @helcoski_growing_2019) and had substantial but not devastating impacts on tree growth (Figs. **1b, 2**). These droughts were classified as severe (1977) or extreme (1966, 1999) according to the PDSI metric and have been linked to tree mortality in the eastern United States [@druckenbrod_redefining_2019]; however, extreme, multiannual droughts or so-called “megadroughts” of the type that have triggered massive tree die-off in other regions (e.g., @allen_global_2010; @stovall_tree_2019) have not occurred in the Eastern United States within the past several decades [@clark_impacts_2016]. Of the droughts considered here, the 1966 drought, which was preceded by two years of dry conditions (Fig. **S2**), severely stressed a larger portion of trees (Fig. **1b**). The tendency for large trees to have lowest resistance was most pronounced in this drought, consistent with other findings that this physiological response increases with drought severity [@bennett_larger_2015; @stovall_tree_2019]. Across all three droughts, the majority of trees experienced reduced growth, but a substantial portion had increased growth (Fig. **1b**), potentially due to decreased leaf area of competitors during the drought (**REF--if we can find one**), and consistent with prior observations that smaller trees can exhibit increased growth rates during drought [@bennett_larger_2015]. It is likely because of the moderate impact of these droughts, along with other factors influencing tree growth (e.g., stand dynamics), that our best models characterize only a modest amount of variation in $Rt$: 11-12% for all droughts combined, and 18-25% for each individual drought (Table S6).

Consistent with studies in other forests worldwide (**REFS**), taller trees in this forest exhibited lower drought resistance. 
Mechanistically, this is consistent with, and reinforces, previous findings that biophysical constraints make it impossible for trees to efficiently transport water to great heights and simultaneously maintain strong resistance and resilience to drought-induced embolism [@olson_plant_2018; @couvreur_water_2018; @roskilly_conflicting_2019]. 
Taller trees also face dramatically different microenvironments (Fig. **3**). 
They are exposed to higher wind speeds and lower humidity (Fig. **3a-b**), resulting in higher evaporative demand (**REFS**). 
Unlike other temperate forests where modestly cooler understory conditions have been documented (**REFS**), particularly under drier conditions (**REFS**), we observed no significant variation in air temperatures across the vertical profile (Fig. **3c**). 
More critically for tree physiology, leaf temperatures can become significantly elevated over air temperature under conditions of high solar radiation and low stomatal conductance (*Campbell & Norman REF*). 
Under drought, when air temperatures tend to be warmer, direct solar radiation tends to be higher (because of less cloud cover), and less water is available for evaporative cooling of the leaves, trees with sun-exposed crowns may not be able to simultaneously maintain leaf temperatures below damaging extremes and avoid drought-induced embolism. 
Indeed previous studies have shown lower drought resistance in more exposed trees [@liu_effect_1993; @suarez_factors_2004; @scharnweber_confessions_2019].
Unfortunately, collinearity between height and crown exposure in this study (Fig. **3d**) makes it impossible to confidently partition causality. 
Additional research comparing drought responses of early successional and mature forest stands, along with short and tall isolated trees, would be valuable for more clearly disentangling the roles of tree height and crown exposure.   
Belowground, taller trees would tend to have larger root systems, but the potentially greater access to water did not override the disadvantage conferred by height--and, in fact, greater moisture access in non-drought years (here, higher TWI) appears to make trees more sensitive to drought [@zuleta_drought-induced_2017; @stovall_tree_2019].
The observed height-sensitivity of $Rt$, together with the lack of advantage to large stature in drier topographic positions, agrees with the concept that physiological limitations to transpiration under drought shift from soil water availability to the plant-atmosphere interface as forests age [@bretfeld_plant_2018], such that tall, dominant trees are the most sensitive in mature forests. 
Again, additional research comparing drought responses across forests with different tree heights and water availability would be valuable for disentangling the relative importance of above- and belowground mechanisms.

*Even under non-drought conditions, evaporative demand and maximum leaf temperatures increase with tree height [@smith_temperature_1977; @bretfeld_plant_2018; @kunert_revised_2017], and such conditions would incur additional stress during drought, when solar radiation tends to be higher and less water is available for evaporative cooling of the leaves .*

The development of tree-ring chronologies for the twelve most dominant tree species at our site [@helcoski_growing_2019; @bourg_initial_2013] gave us the sample size to compare historical drought responses across species (Fig. **2**) and associated traits at a single site [see also @elliott_forest_2015]. 
Our study reinforced the findings of previous studies (see Introduction) that wood density and $LMA$ are not reliably linked to drought resistance (Table 1).
Contrary to previous studies in temperate deciduous forests, we did not find an association between xylem porosity and drought tolerance, as the two diffuse-porous species, *Liriodendron tulipifera* and *Fagus grandifolia*, were at opposite ends of the $Rt$ spectrum (Fig. 2). 
While the low $Rt$ of *L. tulipifera* is consistent with other studies [@elliott_forest_2015], the high $Rt$ of *F. grandifolia* contrasts with studies identifying diffuse porous species in general [@elliott_forest_2015; @kannenberg_linking_2019], and the genus *Fagus* in particular [@friedrichs_species-specific_2009], as drought sensitive.  
There are two potential explanations for this discrepancy.
First, other traits can and do override the influence of xylem porosity on drought resistance. 
Ring porous species are restricted mainly to temperate deciduous forests (*Wheeler et al. 2007*), while highly drought-tolerant diffuse-porous species exist in other biomes (*REFS*). 
*Fagus grandifolia* had intermediate $\pi_{tlp}$ and low $PLA_{dry}$ (Fig. **S4**), which would have contributed to it's drought resistance (Fig. **4**; see discussion below). 
A second explanation of why *F. grandifolia* trees at this particular site had higher $Rt$ is that the sampled individuals, reflective of the population within the plot, are generally shorter and in less dominant canopy positions compared to most other species (Fig. **S4**).
The species, which is highly shade-tolerant, also has deep crowns [@andersonteixeira_size-related_2015], implying that a lower proportion of leaves would be affected by harsher microclimatic conditions at the top of the canopy under drought (Fig. **3**).
Thus, the high $Rt$ of the sampled *F. grandifolia* population can be explained by a combination of fairly drought-resistant leaf traits, shorter stature, and a buffered microenvironment.

@@

### Supplementary Information
Table S1: Species-specific bark thickness regression equations

>>>>

In the years for which we have vertical profiles in climate data (2016-2018), taller trees--or those in dominant crown positions-- were generally exposed to higher evaporative demand during the peak growing season months (May-August; Fig. **2**). Specifically, maximum daily wind speeds were significantly higher above the top of the canopy (40-50m) than within and below (10-30m) (Fig. **2a**). Relative humidity was also somewhat lower during June-August, ranging from ~50-80% above the canopy and ~60-90% in the understory (Fig. **2b**). Air temperature did not vary across the vertical profile (Fig. **2c**).

Crown position varied as expected with height (dominant > co-dominant > intermediate > suppressed), but with substantial variation (Fig. **2d**). 
Correlation between height and canopy position was 0.73.

@@

At the community level, cored trees showed substantial growth reductions in all three droughts, with a mean $Rt$ of 0.86 in 1966 and 1999, and 0.84 in 1977  (Fig. **2b**). Across the entire study period (1950-2009), the focal drought years were the three years with the largest fraction of trees exhibiting $Rt \le 0.7$. Specifically, in each drought, roughly 30% of the cored trees had growth reductions of $\ge$ 30% ($Rt \le 0.7$): 29% in 1966, 32% in 1977, and 27% in 1999. However, some individuals exhibited increased growth, *i.e.*, $Rt > 1.0$: 26% of trees in 1966, 22% in 1977, and 26% in 1999.

Responses varied across species and by drought (Fig. **3**). 
Averaged across all droughts, $Rt$ was lowest in *Liriodendron tulipifera* (mean $Rt$ = **0.66**) and highest in *Fagus grandifolia* (mean $Rt$ = **0.99**).

@@

Wood density, $LMA$, and xylem porosity were all poor predictors of $Rt$ (Tables 1,S4-S5). 
Wood density and $LMA$ were never significantly associated with $Rt$ in the single-variable tests and were therefore excluded from the full models. 
Xylem porosity was also excluded from the full models, as it had no significant influence for all droughts combined and had contrasting effects in the individual droughts: whereas ring-porous species had higher $Rt$ than diffuse- and semi-ring- porous species in the 1966 and 1999 droughts, they had lower $Rt$ in 1977 (Table S4). 
It is noteworthy that the two diffuse-porous species in our study, *Liriodendron tulipifera* and *Fagus grandifolia*, were at opposite ends of the $Rt$ spectrum (Fig. **3**), further refuting the idea that xylem porosity is a useful predictor of $Rt$ in the context of this study.

In contrast, $PLA_{dry}$, and $\pi_{tlp}$ were linked to drought responses (Fig. **4**; Tables 1,S4-S7). 
Both had consistent signs across all droughts and explained modest amounts of variation ($\Delta$AICc > 1.0) during at least one of the three droughts (Table S4), qualifying them as candidate variables for the full model. 
$PLA_{dry}$ had a significant influence, with negative coefficient, in full models for the three droughts combined and for the 1966 drought individually (Fig. **4**; Tables S6-S7). 
For 1977 and 1999, it was included, with negative coefficient, in some of the top models (Tables S6-S7).
$\pi_{tlp}$ was included, with negative coefficient, in the best model for all droughts combined and for the 1977 drought individually (Fig. **4**; Table S6). 
It was included in some of the top models for 1999 (Tables S6-S7).

@@

Tree height, microenvironment, and hydraulic traits shaped tree growth responses across three droughts at our study site (Table 1, Fig. **4**). The greater susceptibility of larger trees to drought, similar to forests worldwide [@bennett_larger_2015], was driven primarily by their height [@stovall_tree_2019]. Taller height was likely a liability in itself, and was also associated with greater exposure to conditions that would promote water loss and heat damage during drought (Fig. **2**). There was no evidence that soil water availability increased drought resistance; in contrast, trees in wetter topographic positions had lower $Rt$ [@zuleta_drought-induced_2017; @stovall_tree_2019], and the larger potential rooting volume of large trees provided no advantage in the drier microenvironments. The negative effect of height on $Rt$ held after accounting for species' traits. Drought resistance was not consistently linked to species' $LMA$, wood density, or xylem type (ring- vs. diffuse porous), but was negatively correlated with leaf hydraulic traits ($PLA_{dry}$, $\pi_{tlp}$). This is the first report to our knowledge linking $PLA_{dry}$ and $\pi_{tlp}$ to growth reduction during drought. The directions of these responses were consistent across droughts (Table S6), supporting the premise that they were driven by fundamental physiological mechanisms. However, the strengths of each predictor varied across droughts (Fig. **4**; Tables S6-S7), indicating that drought characteristics interact with tree size, microenvironment, and traits to shape which individuals are most affected. These findings advance our knowledge of the factors that make trees vulnerable to growth declines during drought--and, by extension, likely make them more vulnerable to mortality [@sapes_plant_2019].

The droughts considered here were of a magnitude that has occurred with an average frequency of approximately once every 10-15 years (Fig. **1a**, @helcoski_growing_2019) and had substantial but not devastating impacts on tree growth (Figs. **1b**). These droughts were classified as severe (1977) or extreme (1966, 1999) according to the PDSI metric and have been linked to tree mortality in the eastern United States [@druckenbrod_redefining_2019]; however, extreme, multiannual droughts or so-called “megadroughts” of the type that have triggered massive tree die-off in other regions (e.g., @allen_global_2010; @stovall_tree_2019) have not occurred in the Eastern United States within the past several decades [@clark_impacts_2016]. Of the droughts considered here, the 1966 drought, which was preceded by two years of dry conditions (Fig. **S2**), severely stressed a larger portion of trees (Fig. **1b**). The tendency for large trees to have lowest resistance was most pronounced in this drought, consistent with other findings that this physiological response increases with drought severity [@bennett_larger_2015; @stovall_tree_2019]. Across all three droughts, the majority of trees experienced reduced growth, but a substantial portion had increased growth (Fig. **1b**), potentially due to decreased leaf area of competitors during the drought (**REF--if we can find one**), and consistent with prior observations that smaller trees can exhibit increased growth rates during drought [@bennett_larger_2015]. It is likely because of the moderate impact of these droughts, along with other factors influencing tree growth (e.g., stand dynamics), that our best models characterize only a modest amount of variation in $Rt$: 11-12% for all droughts combined, and 18-25% for each individual drought (Table S6).

Consistent with studies in other forests worldwide (**REFS**), taller trees in this forest exhibited lower drought resistance. 
Mechanistically, this is consistent with, and reinforces, previous findings that biophysical constraints make it impossible for trees to efficiently transport water to great heights and simultaneously maintain strong resistance and resilience to drought-induced embolism [@olson_plant_2018; @couvreur_water_2018; @roskilly_conflicting_2019]. 
Taller trees also face dramatically different microenvironments (Fig. **2**). 
They are exposed to higher wind speeds and lower humidity (Fig. **2a-b**), resulting in higher evaporative demand (**REFS**). 
Unlike other temperate forests where modestly cooler understory conditions have been documented (**REFS**), particularly under drier conditions (**REFS**), we observed no significant variation in air temperatures across the vertical profile (Fig. **2c**). 
More critically for tree physiology, leaf temperatures can become significantly elevated over air temperature under conditions of high solar radiation and low stomatal conductance (*Campbell & Norman REF*). 
Under drought, when air temperatures tend to be warmer, direct solar radiation tends to be higher (because of less cloud cover), and less water is available for evaporative cooling of the leaves, trees with sun-exposed crowns may not be able to simultaneously maintain leaf temperatures below damaging extremes and avoid drought-induced embolism. 
Indeed previous studies have shown lower drought resistance in more exposed trees [@liu_effect_1993; @suarez_factors_2004; @scharnweber_confessions_2019].
Unfortunately, collinearity between height and crown exposure in this study (Fig. **2d**) makes it impossible to confidently partition causality. 
Additional research comparing drought responses of early successional and mature forest stands, along with short and tall isolated trees, would be valuable for more clearly disentangling the roles of tree height and crown exposure.   
Belowground, taller trees would tend to have larger root systems, but the potentially greater access to water did not override the disadvantage conferred by height--and, in fact, greater moisture access in non-drought years (here, higher TWI) appears to make trees more sensitive to drought [@zuleta_drought-induced_2017; @stovall_tree_2019].
The observed height-sensitivity of $Rt$, together with the lack of advantage to large stature in drier topographic positions, agrees with the concept that physiological limitations to transpiration under drought shift from soil water availability to the plant-atmosphere interface as forests age [@bretfeld_plant_2018], such that tall, dominant trees are the most sensitive in mature forests. 
Again, additional research comparing drought responses across forests with different tree heights and water availability would be valuable for disentangling the relative importance of above- and belowground mechanisms.

*Saving this for references: Even under non-drought conditions, evaporative demand and maximum leaf temperatures increase with tree height [@smith_temperature_1977; @bretfeld_plant_2018; @kunert_revised_2017] .*

The development of tree-ring chronologies for the twelve most dominant tree species at our site [@helcoski_growing_2019; @bourg_initial_2013] gave us the sample size to compare historical drought responses across species (Fig. **3**) and associated traits at a single site [see also @elliott_forest_2015]. 
Our study reinforced the findings of previous studies (see Introduction) that wood density and $LMA$ are not reliably linked to drought resistance (Table 1).
Contrary to previous studies in temperate deciduous forests, we did not find an association between xylem porosity and drought tolerance, as the two diffuse-porous species, *Liriodendron tulipifera* and *Fagus grandifolia*, were at opposite ends of the $Rt$ spectrum (Fig. **3**). 
While the low $Rt$ of *L. tulipifera* is consistent with other studies [@elliott_forest_2015], the high $Rt$ of *F. grandifolia* contrasts with studies identifying diffuse porous species in general [@elliott_forest_2015; @kannenberg_linking_2019], and the genus *Fagus* in particular [@friedrichs_species-specific_2009], as drought sensitive.  
There are two potential explanations for this discrepancy.
First, other traits can and do override the influence of xylem porosity on drought resistance. 
Ring porous species are restricted mainly to temperate deciduous forests (*Wheeler et al. 2007*), while highly drought-tolerant diffuse-porous species exist in other biomes (*REFS*). 
*Fagus grandifolia* had intermediate $\pi_{tlp}$ and low $PLA_{dry}$ (Fig. **S4**), which would have contributed to it's drought resistance (Fig. **4**; see discussion below). 
A second explanation of why *F. grandifolia* trees at this particular site had higher $Rt$ is that the sampled individuals, reflective of the population within the plot, are generally shorter and in less dominant canopy positions compared to most other species (Fig. **S4**).
The species, which is highly shade-tolerant, also has deep crowns [@andersonteixeira_size-related_2015], implying that a lower proportion of leaves would be affected by harsher microclimatic conditions at the top of the canopy under drought (Fig. **2**).
Thus, the high $Rt$ of the sampled *F. grandifolia* population can be explained by a combination of fairly drought-resistant leaf traits, shorter stature, and a buffered microenvironment.

@@

### Supplementary Information

*redo this list!!*

Table S1: Species-specific bark thickness regression equations

### 2020-07-17 manuscript/tables&figures.Rmd
switched figs 2 & 3
#115

**Figure 2. Drought resistance, $Rt$, across species for the three focal droughts.** Drought are color coded as in Fig. 1. Species codes are given in Table 3.

**Figure 3. Height profiles in growing season climatic conditions and tree heights by crown position** Shown are averages ($\pm$ SD) of daily maxima and minima of (**a**) wind speed, (**b**) relative humidity ($RH$), and (**c**) air temperature ($T_{air}$) averaged over each month of the peak growing season (May-August) from 2016-2018. In these plots, heights are slightly offset for visualization purposes. Also shown is (**d**) 2018 tree heights by crown position (see Table 2 for codes). In all plots, the dashed horizontal line indicates the 95th percentile of tree heigts in the ForestGEO plot.

@@

![**Figure 2. Drought resistance, $Rt$, across species for the three focal droughts.** Drought are color coded as in Fig. 1. Species codes are given in Table 3.](tables_figures/publication/Figure2_rt_across_sp.png){width=500px}

@@

![**Figure 3. Height profiles in growing season climatic conditions and tree heights by crown position.** The top row shows averages ($\pm$ SD) of daily maxima and minima of (a) wind speed, (b) relative humidity ($RH$), and (c) air temperature ($T_{air}$) averaged over each month of the peak growing season (May-August) from 2016-2018. In these plots, heights are slightly offset for visualization purposes. Also shown is (d) 2018 tree heights by crown position (see Table 2 for codes). In all plots, the dashed horizontal line indicates the 95th percentile of tree heigts in the ForestGEO plot.](tables_figures/publication/Figure3_NEON_vars_height_profile.png){width=500px}

>>>>

**Figure 2. Contemporary height profiles in sun exposure and growing season microclimate under non-drought conditions.** Shown are average ($\pm$ SD) of daily maxima and minima of (a) wind speed, (b) relative humidity ($RH$), and (c) air temperature ($T_{air}$) averaged over each month of the peak growing season (May-August) from 2016-2018. In these plots, heights are slightly offset for visualization purposes. Also shown is (d) tree heights by 2018 crown position. In all plots, the dashed horizontal line indicates the 95th percentile of tree heigts in the ForestGEO plot.

**Figure 3. Drought resistance, $Rt$, across species for the three focal droughts.** Species codes are given in Table 2.

@@

![**Figure 2. Contemporary height profiles in sun exposure and growing season microclimate under non-drought conditions.** Shown are average ($\pm$ SD) of daily maxima and minima of (a) wind speed, (b) relative humidity ($RH$), and (c) air temperature ($T_{air}$) averaged over each month of the peak growing season (May-August) from 2016-2018. In these plots, heights are slightly offset for visualization purposes. Also shown is (d) tree heights by 2018 crown position. In all plots, the dashed horizontal line indicates the 95th percentile of tree heigts in the ForestGEO plot.](tables_figures/publication/Figure3_NEON_vars_height_profile.png){width=500px}

@@

![**Figure 3. Drought resistance, $Rt$, across species for the three focal droughts.** Species codes are given in Table 2.](tables_figures/publication/Figure2_rt_across_sp.png){width=500px}
